Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2023-07-19 ba_resubmit/response_to_reviewers2.tex

%\reply{%
%	
%	We have switched the order of Sections 4.2 and 4.3, so that we first discuss hashing, then posterior inference, then chunkwise computation of the comparison matrix, and then SEI. With this new ordering, and with the newly provided equations (15 -19) it is clearer that the contribution of \emph{all} record pairs is recorded through the summary statistics in $\mathcal{N}$.
%}

\pointRaised{R}{%
	Second paragraph of Section 4.2: “and delete those comparison vectors”. Which are “those” vectors?}

	\reply{

%	In the revised paper, ``vector" is replaced with ``matrix" when referring to $\gamma.$ (See R.13 regarding making the paper consistent below).

	\textcolor{teal}{In the original manuscript, ``those comparison vectors" refer to removing the larger (and expensive) $\Gamma^{ab}$ from memory and continuing our calculations with the compressed comparison vectors $\tilde{\Gamma}^{ab}.$ }

	\textcolor{teal}{The revised text states: ``Then, we conduct hashing, obtain the compressed comparison matrix, $\tilde{\gamma}^{ab}$, and remove the memory-intensive comparison matrix, $\gamma^{ab}$, before continuing with the next chunk of data. See Section 4.3, page 10. }

%	 \textcolor{red}{Question for Brian: is lowercase $\gamma$ always a matrix? Let's make sure we're not swapping between vectors and matrices. In the previous version this was a vector and now its listed as a matrix. I would argue that a matrix should use capital notation, such as $\Gamma.$}
	}

@@

\pointRaised{R}{%
Equations (8) and (9): Should the weights have superscript (s) (as the Zs do)?}

\reply{%
	This has been fixed. 
}

\pointRaised{R}{%
	Gamma is in some places described as a set and in others as a matrix (particularly in sections 4.2 and 5.1).
}

\reply{%
	\textcolor{teal}{Note that $\gamma$ is a comparison matrix comprised by comparison vectors. All references to $\gamma$ as a set have been removed. See Section 2, page 3, where we define both the comparison vector and comparison matrix.}
}

### 2023-07-19 ba_resubmit/kundinger_resubmit2.tex
working on response to reviewers.

Intuitively, matching records (those that refer to the same entity) should have similar values of the linking variables; records that are nonmatching should have dissimilar values. \cite{fellegi_theory_1969} proposed encoding this using a comparison vector $\gamma_{ij}$ computed for each record pair $(i,j)$ in $A \times B.$  Specifically, they define $\gamma_{ij} = (\gamma_{ij}^1, \ldots, \gamma_{ij}^F),$ where each $\gamma_{ij}^f$ is a value indicating the similarity of field $f$ for records $A_i$ and $B_j$. For notational convenience, we define the comparison matrix $\gamma \in \mathbb{R}^{n_A n_B F}$ as the collection of all record pairs' $\gamma_{ij}$.

>>>>

Intuitively, matching records (those that refer to the same entity) should have similar values of the linking variables; records that are nonmatching should have dissimilar values. \cite{fellegi_theory_1969} proposed encoding this using a comparison vector $\gamma_{ij}$ computed for each record pair $(i,j)$ in $A \times B.$  Specifically, they define a \emph{comparison vector} $\gamma_{ij} = (\gamma_{ij}^1, \ldots, \gamma_{ij}^f, \ldots \gamma_{ij}^F),$ where each $\gamma_{ij}^f$ is a value indicating the similarity of field $f$ for records $A_i$ and $B_j$. For notational convenience, we define the \emph{comparison matrix} $\gamma \in \mathbb{R}^{n_A n_B F}$ as the collection of all record pairs' $\gamma_{ij}$.
